---
title: "test for html"
output: html_document
css: "my1.css"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r klippy, echo=FALSE, include=TRUE}
klippy::klippy(position=c("top","right"))
```
 <div class="part1">
<div class="tab">
<button class="tablinks button" onClick="location.href='my2.html'">Test for movement</button> 
 </div>
  </div>


## R Markdown



```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.





<ul id="ProjectSubmenu">
    <li><a href="/projects/markdown/" title="Markdown Project Page">Main</a></li>
    <li><a href="/projects/markdown/basics" title="Markdown Basics">Basics</a></li>
    <li><a class="selected" title="Markdown Syntax Documentation">Syntax</a></li>
    <li><a href="/projects/markdown/license" title="Pricing and License Information">License</a></li>
    <li><a href="/projects/markdown/dingus" title="Online Markdown Web Form">Dingus</a></li>
</ul>


*   [Overview](#overview)
    *   [Philosophy](#philosophy)
    *   [Inline HTML](#html)
    *   [Automatic Escaping for Special Characters](#autoescape)
*   [Block Elements](#block)
    *   [Paragraphs and Line Breaks](#p)
    *   [Headers](#header)
    *   [Blockquotes](#blockquote)
    *   [Lists](#list)
    *   [Code Blocks](#precode)
    *   [Horizontal Rules](#hr)
*   [Span Elements](#span)
    *   [Links](#link)
    *   [Emphasis](#em)
    *   [Code](#code)
    *   [Images](#img)
*   [Miscellaneous](#misc)
    *   [Backslash Escapes](#backslash)
    *   [Automatic Links](#autolink)

